Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-02 review_article.Rmd
Map methods table

To choose an appropriate map display, the map creator must consider the intended user, and message the map will communicate.
To discover whether the display is appropriate, consider the  
Techonology has played an enormous role in increasing the opportunities for map makers.
The computation and graphics power have made creation, alteration and interactivity possible.
The internet has made communication of scientific data and results increasingly accessible.
Creating maps of dieases now involves more decisions as these options have expanded and it is the objectives of the investigator that will drive the choices. @CPISACA and @SAMGIS have provided suggestions and comments to help map creators best communicate their health data and spatial analyses.

<!-- Choropleths, true topology, geographic distance, good for showing geographic importance -->
Visualisation properties have been explored across several disease mapping displays.
Choropleth displays utilise more traditional cartographic methods, this means they are usually true to the topography.
Tobler's work highlights the need for consideration of the transformation of the globe to a 2D space.
When there is a relationship between the cancer type being mapped and geographical features, a choropleth map would pair this information visually.
These maps are best used when the geography is of importance to the data in the display.
Users can identify the areas relevant to them by the familiar boundaries, and can easily contrast the experience of geographic neighbours.

@@

>>>>

<!-- Choropleths, true topology, geographic distance, good for showing geographic importance -->
Visualisation properties have been explored across several disease mapping displays.
To choose an appropriate map display, the map creator must consider the intended user, and message the map will communicate.
Choropleth displays utilise more traditional cartographic methods, they are usually true to the topography, displaying familiar boundaries of countries, states or administrative areas.
Choropleth methods require a decision to be made about the projection of the display, in this case aim to find a map projection that gives the least distorted representation of the geography [@UMPT].
When there is a relationship between the cancer type being mapped and geographical features, a choropleth map would pair this information visually.
These maps are best used when the geography is of importance to the data in the display.
Users can identify the areas relevant to them by the familiar boundaries, and can easily contrast the experience of geographic neighbours.

@@

Table: \label{tab:methods} Mapping methods used to display cancer statistics

|  | Choropleth | Contiguous Cartogram | Non-contiguous Cartogram | Dorling | Tilegrams |
|:---------------------------------------------------:|------------|----------------------|--------------------------|---------|-----------|
| Feature Preservation: |  |  |  |  |  |
| Preserves shapes | Y | N | Y | N | N |
| Preserves neighbours | Y | Y | Y | S | S |
| Uniform use of shape | N | N | N | Y | Y |
| Statistical transformation of the base map: |  |  |  |  |  |
| Used for Bi-variate maps eg. population & statistic | N | Y | Y | Y | Y |
|  |  |  |  |  |  |

Creating maps of dieases now involves more decisions to be made by map makers, rather than cartographers. 
Techonology has played an enormous role in increasing the opportunities for map makers.
The computation and graphics power have made creation, alteration and interactivity possible.
as these options have expanded and it is the objectives of the investigator that will drive the choices. @CPISACA and @SAMGIS have provided suggestions and comments to help map creators best communicate their health data and spatial analyses.
